**skater**: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-11-30 paper/paper.Rmd
fix abstract

---
title: "**skater**: An R package for SNP-based Kinship Analysis, Testing, and Evaluation"
author: 
  - name: Stephen D. Turner
    affiliation: Signature Science, LLC., Austin, TX 78759, USA.
  - name: V. P. Nagraj
    affiliation: Signature Science, LLC., Austin, TX 78759, USA.
  - name: Matthew Scholz
    affiliation: Signature Science, LLC., Austin, TX 78759, USA.
  - name: Shakeel Jessa
    affiliation: Signature Science, LLC., Austin, TX 78759, USA.
  - name: Carlos Acevedo
    affiliation: Signature Science, LLC., Austin, TX 78759, USA.
  - name: Jianye Ge
    affiliation: Center for Human Identification, Department of Microbiology, Immunology, and Genetics, University of North Texas Health Science Center, Fort Worth, TX 76107, USA. 
  - name: August E. Woerner
    affiliation: Center for Human Identification, Department of Microbiology, Immunology, and Genetics, University of North Texas Health Science Center, Fort Worth, TX 76107, USA. 
  - name: Bruce Budowle
    affiliation: Center for Human Identification, Department of Microbiology, Immunology, and Genetics, University of North Texas Health Science Center, Fort Worth, TX 76107, USA. 
# Abstract up to 300 words. No citations, minimal abbreviations.
abstract: | 
    | 
    | **Motivation:** SNP-based kinship analysis with genome-wide relationship estimation and IBD segment analysis methods produces results that often require further downstream processing and manipulation. A dedicated software package that consistently and intuitively implements this analysis functionality is needed.  
    | **Results:**  Here we present the skater R package for **S**NP-based **k**inship **a**nalysis, **t**esting, and **e**valuation with **R**. The skater package contains a suite of well-documented tools for importing, parsing, and analyzing pedigree data, performing relationship degree inference, benchmarking relationship degree classification, and summarizing IBD segment data.  
    | **Availability:** The skater package is implemented as an R package and is released under the MIT license at https\:\/\/github.com/signaturescience/skater. Documentation is available at https\:\/\/signaturescience.github.io/skater.
keywords: bioinformatics, kinship, R, genealogy, SNPs, single nucleotide polymorphisms, relatedness
bibliography: bibliography.bib
output: BiocWorkflowTools::f1000_article
---

>>>>

---
title: '**skater**: An R package for SNP-based Kinship Analysis, Testing, and Evaluation'
author:
- name: Stephen D. Turner
  affiliation: Signature Science, LLC., Austin, TX 78759, USA.
- name: V. P. Nagraj
  affiliation: Signature Science, LLC., Austin, TX 78759, USA.
- name: Matthew Scholz
  affiliation: Signature Science, LLC., Austin, TX 78759, USA.
- name: Shakeel Jessa
  affiliation: Signature Science, LLC., Austin, TX 78759, USA.
- name: Carlos Acevedo
  affiliation: Signature Science, LLC., Austin, TX 78759, USA.
- name: Jianye Ge
  affiliation: Center for Human Identification, Department of Microbiology, Immunology,
    and Genetics, University of North Texas Health Science Center, Fort Worth, TX
    76107, USA.
- name: August E. Woerner
  affiliation: Center for Human Identification, Department of Microbiology, Immunology,
    and Genetics, University of North Texas Health Science Center, Fort Worth, TX
    76107, USA.
- name: Bruce Budowle
  affiliation: Center for Human Identification, Department of Microbiology, Immunology,
    and Genetics, University of North Texas Health Science Center, Fort Worth, TX
    76107, USA.
abstract: | 
    | 
    | **Motivation:** SNP-based kinship analysis with genome-wide relationship estimation and IBD segment analysis methods produces results that often require further downstream processing and manipulation. A dedicated software package that consistently and intuitively implements this analysis functionality is needed.  
    | **Results:**  Here we present the skater R package for **S**NP-based **k**inship **a**nalysis, **t**esting, and **e**valuation with **R**. The skater package contains a suite of well-documented tools for importing, parsing, and analyzing pedigree data, performing relationship degree inference, benchmarking relationship degree classification, and summarizing IBD segment data.  
    | **Availability:** The skater package is implemented as an R package and is released under the MIT license at https\:\/\/github.com/signaturescience/skater. Documentation is available at https\:\/\/signaturescience.github.io/skater.
output:
  BiocWorkflowTools::f1000_article: default
bibliography: bibliography.bib
keywords: bioinformatics, kinship, R, genealogy, SNPs, single nucleotide polymorphisms, relatedness
---
